What do incoming university students believe about open science practices in

### 2022-01-20 analysis/Manuscript.Rmd
ToP R and R initial changes

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
  - name: Jennifer L. Beaudry
    affiliation: '1,4'
    role:
      - Conceptualization
      - Data curation
      - Formal analysis
      - Investigation
      - Methodology
      - Project administration
      - Validation
      - Visualization
      - Writing - original draft
      - Writing - review & editing
    corresponding: yes
    email: jen.beaudry@flinders.edu.au
    address: Research Development and Support, Flinders University, Bedford Park, 5042
  - name: Matt N. Williams
    affiliation: '2'
    role:
      - Investigation
      - Methodology
      - Validation
      - Writing - original draft
    email: m.n.williams@massey.ac.nz
  - name: Michael C. Philipp
    affiliation: '2'
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Project administration
      - Writing - original draft
    email: m.philipp@massey.ac.nz
  - name: Emily J. Kothe
    affiliation: '3'
    role:
      - Conceptualization
      - Data curation
      - Validation
      - Visualization
      - Writing - review & editing
    email: emily.kothe@deakin.edu.au

affiliation:
  - id: '1'
    institution: Flinders University, Australia
  - id: '2'
    institution: Massey University, New Zealand
  - id: '3'
    institution: Deakin University, Australia
  - id: '4'
    institution: Swinburne University of Technology, Australia

shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default

acknowledgement: |
  The idea of this research was conceived at the 2018 UQ Open Science Conference and further developed at the 2019 Society for the Improvement of Psychological Science Unconference, What do first year psychology students think about (open) science?
  Our special thanks to those who contributed to the data collection effort including: Benjamin Le, Katie Gilligan-Lee, Annayah Prosser, Ian Fairholm, Jennie Ferrell, Kait Clark, Catherine Orr, Nick Burns, Rachel Searston, Rachel Stephens, Matthew Thompson, Aaron Drummond, Kathryn McGuigan, and Peter Cannon.
# will enter this manually on the word document

abstract: |
 Background: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to students’ existing understandings.
 Objective: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
 Method: International online survey with participants who were about to start their first course in psychology at a university (N = 239).
 Results: When asked about how research *should* be done, most students endorsed most (but not all) of ten open science practices. When asked to estimate the proportion of published psychological studies that apply each of a set of 10 open science practices, participants' estimates tended to average near 50%. Only 18% of participants had heard of the term "replication crisis".
 Conclusion: Despite relatively significant media attention on the replication crisis, few incoming psychology students are familiar with the term. Incoming students nevertheless appear to be sympathetic toward most open science practices, although they may overestimate the prevalence of these practices in psychology.
 Teaching Implications: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.

keywords: open science, psychology, teaching, reproducibility, replication
wordcount: (need to update)
bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: no
draft: no
documentclass: apa6
classoption: man
editor_options: 
  chunk_output_type: console
csl: "apa.csl" 
---

@@

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018]. These apparent problems with replication have led to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@wigboldusEncouragePlayingData2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018]. These calls for more reproducible and transparent research practices have prompted the discipline to reflect on and measure researchers' norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @beaudry_swinburne_2019; @harrisUseReproducibleResearch2018].

The most comprehensive set of principles for how science *ought* to be practiced are Merton's norms of science [@mertonNoteScienceDemocracy1942]. Scientists [@andersonExtendingMertonianNorms2010] and graduate students [@andersonGraduateStudentExperience1994] alike have historically endorsed the normative value of Merton's principles. Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms [see @vazireWeWantBe2019; @vazireWhereAreSelfcorrecting2020]. For example, the practices of sharing preprints for open peer review and posting open data for reproducibility checks corresponds to the norms of *communality* and *organised skepticism*: Scientific claims should be openly subjected to critical scrutiny. Preregistration can be connected to the norm of *disinterestedness*: By making preregistered decisions about how to analyse data before results are produced, a researcher limits the degree to which substantive results produced by different analytic strategies affect their decisions regarding about analyses to report.

@@

Second, anecdotal evidence suggests that students being taught about open science practices and reproducibility reforms (such as open sharing of data and analysis code) are sometimes surprised that these are not *already* standard practice. This could imply a need for educators to reinforce and build on students' “naive” impressions rather than radically altering their understanding of how science should be done. On the other hand, some evidence suggests that undergraduate students may quickly begin to engage in practices that hamper reproducibility. For example, @moranKnowItBad2021 found that 26.5% of the undergraduate students in their Canadian sample admitted to “Conducting multiple statistical analyses on the same dataset in an attempt to find a statistically significant result” (p. 14; i.e., *p*-hacking), while 9.6% reported rounding down *p*-values to meet a significance threshold. The extent to which incoming psychology students may---or may not---be “naive open scientists” is useful knowledge for guiding pedagogical approaches.

We therefore conducted a descriptive study, asking incoming undergraduate psychology students about their beliefs regarding reproducibility and open science practices in psychology. Our survey encompassed questions concerning norms (how students felt research *should* be conducted), norms in practice (how students believe psychological research *is* conducted), and replicability (how replicable students believe psychological research is). Our study was exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and did not involve the specification or testing of hypotheses. We preregistered the exploratory nature of this study at https://tinyurl.com/4p64mvwp [blinded].

# Methods
Our materials, data, and analysis script are available at https://tinyurl.com/yz76f4s6 [blinded].

@@

Contacts from tertiary institutions in Australia, New Zealand, the UK, and the USA invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics. An invitation was sent to participants via email or a course website 1–2 weeks before their course began. The invitation specified that student needed to be 18 years or older and starting their first course/unit of study in psychology at a university within the following month and included a link to the survey.

@@

Our approach to measuring norms and counternorms focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf. Anderson et al., 2007). <!-- Mention here our discussions workshopping of common open science norms at SIPs? JB: I think we have to, don't we?-->
The ten practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficient information of replicability, preprints, open materials, open data, and open access publishing. Although we acknowledge the merits of some of these practices are debatable [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.

Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." (see Table \@ref(tab:normcounternormitems)). Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.

@@

*Note*: Participants responded to each item in the context of the scenario, “Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis.” Responses were provided on a Likert-type response scale ranging from (strongly disagree) to 5 (strongly agree).

@@

In general, the students seemed to endorse open science practices: For seven of the ten open science practices, agreement with the norm item was stronger than for the corresponding counternorm. However, the extent to which participants endorsed open science norms varied substantially across different practices. Participants most strongly endorsed norms that researchers should provide sufficient information about studies to permit replicability, be critical of published findings, and avoid p-hacking (means > 4; 4 representing 'agree'). They also tended to agree that researchers should avoid HARKing, share papers as open access, share open materials, and preregister their studies; the means for these items varied between 3.5 and 4. On the other hand, they tended to disagree with the practice of sharing preprints prior to peer review and, to a lesser extent, with sharing open data.

@@

Participants who indicated they had heard of the replication crisis were asked, "What do you think 'the replication crisis' is"? Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most provided responses roughly consistent with the conventional interpretation of the term. Example responses included, "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated". Only `r sum(crisis_descriptions$Accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").

@@

Despite efforts to improve the replicability of research over the past decade, and corresponding media attention, most incoming psychology students in our sample were unaware of the replication crisis. Encouragingly, on the other hand, most tended to endorse open science norms more-so than counternorms. Notably this wasn't the case for all open science practices (namely sharing of pre-prints and open data). It may well be that scientific training has enshrined peer review as an essential practice that is robust to change.

@@

The fact that the mean estimated prevalence was no higher than 64% for any practice is inconsistent with the sometime-reported claim that incoming students tend to naively assume that science is *usually* conducted openly. Nevertheless, the students appear to have at least somewhat over-estimated the prevalence of some open science practices. For example, on average students estimated that nearly a third of published psychological studies share data openly and that nearly half of studies are preregistered. In contrast, an examination of a random sample of 250 psychology articles published between 2014 and 2017 [@hardwickeEstimatingPrevalenceTransparency2021] found that just 2% shared open data and 3% were preregistered.

## Strengths and Limitations
Despite a relatively large sample size, our results provide an imperfect picture of new psychology students’ methodological understandings. Our use of convenience samples coupled with the imprecision of polling students’ impressions at one point in time suggest that we can make only tentative generalisations to a wider population of incoming psychology students. However, collectively these results demonstrate some clear topics that might be targeted in our teaching: for example, emphasising the value of pre-prints and open data to research practice.

@@

@@

## Conclusion and Teaching Implications
Overall these findings suggest that incoming psychology students have a degree of sympathy for open science norms. Nevertheless, despite significant media attention on the replication crisis, few have heard of this crisis. Similarly, students seemed to be relatively unfamiliar with responses to the replication crisis (e.g., open science practices). It is therefore important that teachers of psychology not assume pre-existing knowledge among incoming students.

For teachers interested in systematically surveying their students' existing understanding of open science practices in psychology, our survey questions could be a useful resource. These questions are available at https://tinyurl.com/yz76f4s6 [blinded].

>>>>

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
  - name: Jennifer L. Beaudry
    affiliation: '1,4'
    role:
      - Conceptualization
      - Data curation
      - Formal analysis
      - Investigation
      - Methodology
      - Project administration
      - Validation
      - Visualization
      - Writing - original draft
      - Writing - review & editing
    corresponding: yes
    email: jen.beaudry@flinders.edu.au
    address: Research Development and Support, Flinders University, Bedford Park, 5042
  - name: Matt N. Williams
    affiliation: '2'
    role:
      - Investigation
      - Methodology
      - Validation
      - Writing - original draft
    email: m.n.williams@massey.ac.nz
  - name: Michael C. Philipp
    affiliation: '2'
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Project administration
      - Writing - original draft
    email: m.philipp@massey.ac.nz
  - name: Emily J. Kothe
    affiliation: '3'
    role:
      - Conceptualization
      - Data curation
      - Validation
      - Visualization
      - Writing - review & editing
    email: emily.kothe@deakin.edu.au
affiliation:
  - id: '1'
    institution: Flinders University, Australia
  - id: '2'
    institution: Massey University, New Zealand
  - id: '3'
    institution: Deakin University, Australia
  - id: '4'
    institution: Swinburne University of Technology, Australia
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default
acknowledgement: |
  The idea of this research was conceived at the 2018 UQ Open Science Conference and further developed at the 2019 Society for the Improvement of Psychological Science Unconference, What do first year psychology students think about (open) science?
  Our special thanks to those who contributed to the data collection effort including: Benjamin Le, Katie Gilligan-Lee, Annayah Prosser, Ian Fairholm, Jennie Ferrell, Kait Clark, Catherine Orr, Nick Burns, Rachel Searston, Rachel Stephens, Matthew Thompson, Aaron Drummond, Kathryn McGuigan, and Peter Cannon.
abstract: |
 Background: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to students’ existing understandings.
 Objective: We aimed to describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
 Method: An international online survey was conducted with participants who were about to start their first course in psychology at a university (*N* = 239).
 Results: When asked about how research should be done, most students endorsed most (but not all) of ten open science practices. When asked to estimate the proportion of published psychological studies that apply each of a set of 10 open science practices, participants' estimates tended to average near 50%. Only 18% of participants had heard of the term "replication crisis".
 Conclusion: Despite relatively significant media attention on the replication crisis, few incoming psychology students in our sample were familiar with the term. The students were nevertheless sympathetic toward most open science practices, although they appeared to overestimate the prevalence of some of these practices in psychology.
 Teaching Implications: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.
keywords: open science, psychology, teaching, reproducibility, replication
wordcount: (need to update)
bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: no
draft: no
documentclass: apa6
classoption: man
editor_options: 
  chunk_output_type: console
csl: "apa.csl" 
---

@@

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018]. These apparent problems with replication have led to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@wigboldusEncouragePlayingData2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018]. These calls for more reproducible and transparent research practices have prompted the discipline to reflect on and measure researchers' norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @beaudrySwinburneOpenScience2019; @harrisUseReproducibleResearch2018].

@@

Second, anecdotal evidence suggests that students being taught about open science practices and reproducibility reforms (such as open sharing of data and analysis code) are sometimes surprised that these are not already standard practice. This could imply a need for educators to reinforce and build on students' “naive” impressions rather than radically altering their understanding of how science should be done. On the other hand, some evidence suggests that undergraduate students may quickly begin to engage in practices that hamper reproducibility. For example, @moranKnowItBad2021 found that 26.5% of the undergraduate students in their Canadian sample admitted to “Conducting multiple statistical analyses on the same dataset in an attempt to find a statistically significant result” (p. 14; i.e., *p*-hacking), while 9.6% reported rounding down *p*-values to meet a significance threshold. The extent to which incoming psychology students may---or may not---be “naive open scientists” is useful knowledge for guiding pedagogical approaches.

We therefore conducted a descriptive study, asking incoming undergraduate psychology students about their beliefs regarding reproducibility and open science practices in psychology. Our survey encompassed questions concerning norms (how students felt research should be conducted), norms in practice (how students believe psychological research is conducted), and replicability (how replicable students believe psychological research is). Our study was exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and did not involve the specification or testing of hypotheses.

# Methods
We preregistered the exploratory nature of this study at https://tinyurl.com/4p64mvwp [blinded]. Our materials, data, and analysis script are available at https://osf.io/fz6ya/?view_only=51769fc1de304ad3ba0e12a26494ac40 [blinded].

@@

Contacts from tertiary institutions in Australia, New Zealand, the UK, and the USA invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics. These contacts were identified via several avenues, including a dedicated session at the Society for the Improvement of Psychological Science 2019 annual conference, a Twitter thread, and by contacting colleagues of the research team. Although we did not have any specific inclusion criteria with respect to country, although [most? all?] of the contacts who advertised the study were from the United Kingdom, Australia, or New Zealand.

Each contact then sent their students invitations to participate via email or a course website 1–2 weeks before their course began. The invitation specified that student needed to be 18 years or older and starting their first course/unit of study in psychology at a university within the following month and included a link to the survey. The measures and items in the survey were presented in the same order for all participants.

@@

Our approach to measuring norms and counternorms focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms. <!-- Mention here our discussions workshopping of common open science norms at SIPs? JB: I think we have to, don't we?-->
The ten practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficient information of replicability, preprints, open materials, open data, and open access publishing. Although we acknowledge the merits of some of these practices are debatable [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.

Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." (see Table \@ref(tab:normcounternormitems)). Participants rated their agreement with each prescriptive statement on a 1 (*strongly disagree*) to 5 (*strongly agree*) scale. We used the scenario of a specific researcher rather than referring to psychology researchers in general in an attempt to make the questions more concrete and engaging, and because referring to a single named researcher made it easier to construct short and clear items.

@@

*Note*: Participants responded to each item in the context of the scenario, “Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis.” Responses were provided on a Likert-type response scale ranging from 1 (*strongly disagree*) to 5 (*strongly agree*).

@@

In general, the students seemed to endorse open science practices: For seven of the ten open science practices, agreement with the norm item was stronger than for the corresponding counternorm. However, the extent to which participants endorsed open science norms varied substantially across different practices. Participants most strongly endorsed norms that researchers should provide sufficient information about studies to permit replicability, be critical of published findings, and avoid p-hacking (means > 4; 4 representing '*agree*'). They also tended to agree that researchers should avoid HARKing, share papers as open access, share open materials, and preregister their studies; the means for these items varied between 3.5 and 4. On the other hand, they tended to disagree with the practice of sharing preprints prior to peer review and, to a lesser extent, with sharing open data.

@@

Participants who indicated they had heard of the replication crisis were asked, "What do you think 'the replication crisis' is"? Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most (`r sum(crisis_descriptions$Accurate =="y")/length(df$crisis_text[is.na(df$crisis_text)==FALSE])*100`%) provided responses consistent with the conventional interpretation of the term (i.e., describing a realisation that some or many scientific findings cannot be replicated). Example responses included, "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated". Only `r sum(crisis_descriptions$Accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").

@@

Despite efforts to improve the replicability of research over the past decade, and corresponding media attention, most incoming psychology students in our sample were unaware of the replication crisis. Encouragingly, on the other hand, most tended to endorse open science norms more-so than counternorms. Notably this was not the case for all open science practices (namely sharing of pre-prints and open data). It may well be that scientific training has enshrined peer review as an essential practice that is robust to change.

@@

The fact that the mean estimated prevalence was no higher than 64% for any practice is inconsistent with the sometime-reported claim that incoming students tend to naively assume that science is usually conducted openly. Nevertheless, the students appear to have at least somewhat over-estimated the prevalence of some open science practices. For example, on average students estimated that nearly a third of published psychological studies share data openly and that nearly half of studies are preregistered. In contrast, an examination of a random sample of 250 psychology articles published between 2014 and 2017 [@hardwickeEstimatingPrevalenceTransparency2021] found that just 2% shared open data and 3% were preregistered.

## Strengths and Limitations
Despite a relatively large sample size, our results provide an imperfect picture of new psychology students’ methodological understandings. Our use of convenience samples coupled with the imprecision of polling students’ impressions at one point in time suggest that we can make only tentative generalisations to a wider population of incoming psychology students. In particular, the fact that our sample was relatively small and mostly comprised of students from Australia or the United Kingdom limits the extent to which our findings can be generalised to other populations.

@@

While we have interpreted our findings with respect to the norm and counternorm items as reflecting the students' personal endorsement of practices, it is plausible that their responses may have also been affected by their perceptions of what we might perceive as the "right" answers. Differences between endorsement of norms and counternorms may have also been affected by wording differences between the matched options; for example, the HARKing, information for replicability, and p-hacking counternorm items included the phrase "good scientific practice" whereas their matched norm items did not. More broadly, our choices of terminology in constructing items are very likely to have affected participants' responses to some degree. For example, the reference to keeping data "protected" in the open data counternorm item may have nudged participants towards endorsing this item, since failing to "protect" participants' data might sound irresponsible.

We did not investigate the degree to which results differed according to whether or not participants had studied psychology in high school, although interested readers could do so using our open data.

@@

## Conclusion and Teaching Implications
Overall these findings suggest that the incoming psychology students had a degree of sympathy for open science norms. Nevertheless, despite significant media attention on the replication crisis, few had heard of this crisis. Similarly, the students seemed to be relatively unfamiliar with responses to the replication crisis (e.g., open science practices). It is therefore important that teachers of psychology not assume pre-existing knowledge among incoming students.

For teachers interested in systematically surveying their students' existing understanding of open science practices in psychology, our survey questions could be a useful resource. These questions are available at https://osf.io/fz6ya/?view_only=51769fc1de304ad3ba0e12a26494ac40 [blinded].
